Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix ;for the functions: get_log1, print_log1.

Builds a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1) argument.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1)  argument.

@@

Prints a string formed from the template passed in the [msg_template](#func.print_log1.args.msg_template) argument using the format value specified by the [arg1](#func.print_log1.args.arg1).

@@

::: { #func.print_log1.args.msg_template .sidebar }
  - **msg_template:**Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.print_log1.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log1.args.msg_template) argument.

@@

This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.

@@

Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:

  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg] argument;

>>>>

Creates a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument, using the value specified by the [arg1](#func.get_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument, using the value specified by the [arg1](#func.get_log1.args.arg1)  argument to replace all the occurrences of the pattern `%1` found in the template.

@@

Prints a log created from the template passed in the [msg_template](#func.print_log1.args.msg_template) argument, using the value specified by the [arg1](#func.print_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.

@@

::: { #func.print_log1.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.print_log1.args.arg1) argument.

@@

::: { #func.print_log1.args.arg1 .sidebar }
  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.print_log1.args.msg_template) argument.

@@

This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log1](#func.get_log1) function (also called internally) described above.

@@

A glue object, returned by the internally called function [get_log1](#func.get_log1) described above.
:::

@@

Builds a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:

  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg](#func.msg.set_arg.args.arg) argument;
